Approximation as Differentiation notes

### 2025-02-10 notes.tex
nonacm.

\documentclass{acmart}

@@

For a functor $F: C \to Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ with $I$ an object of $C$ and $X \in FI$ an $I$-indexed family;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

>>>>

\documentclass[nonacm]{acmart}

@@

For a functor $F: C \to \Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $C$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}
